---
title: Literature Review: Climate Smart Ag Links to Ecosystem Services
author: MK Lau
---

# Data Pipeline Design

- Compile search terms 
- Assess search term relevance [litsearchr]
  - Access literature [rcrossref]
- Search literature [EBSCO Search Premier]
- Analyze literature results [bibliometrix]
  - Analyze content for intersection with Hawai‘i agriculture
  - Key cross-terms: tropic, hawaii, pacific, island, ... 
- Create a dashboard [Shiny]
- Host dashboard [RShiny]

# Search Terms

Develop a list from the most recent reviews of climate smart
agriculture. 

- climate smart agriculture
- csa
- climate smart commodity
- csc
- climate change
- agroecology
- sustainable agriculture
- nrcs
- conservation
- soil health

```{r setup, echo = FALSE}

library(pacman)
p_load(litsearchr, rcrossref, purrr)
## p_load(litsearchr, rcrossref, purrr, bibliometrix)

```
## *litsearchr* workflow

1. Identifies potential keywords through the naive search input
2. Builds a keyword co-occurrence network to increase search precision
3. Uses a cutoff function to identify keyword importance
4. Assists with grouping terms into concepts
5. Writes a Boolean search 


## rcrossref

https://www.pauloldham.net/api-resources-for-scientific-literature/
https://ciakovx.github.io/rcrossref.html

```{r cr-example, eval = FALSE}

qs <- c("climate smart agriculture")
res <- cr_works(query = qs, limit = 100) %>% pluck("data")
names(res)
res.csa <- res %>% dplyr::select(title, doi, volume, 
                                 issue, page, issued, 
                                 url, publisher, reference.count,
                                 type, abstract, issn)
test <- cr_cn(pluck(res[, "doi"], 1), format = "text", style = "chicago-note-bibliography")

```




# analysis

bibliometrix


## R Tools

- https://elizagrames.github.io/litsearchr/#tutorials 
- https://www.bibliometrix.org/home/index.php/layout/bibliometrix 
- https://www.harc-hspa.com/climate-smart-agriculture.html 
- https://github.com/elizagrames/topictagger 
- https://github.com/cran/metagear 
- https://cran.r-project.org/web/packages/scholar/index.html 

