---
title: Literature Review: Climate Smart Ag Links to Ecosystem Services
author: MK Lau
---

# Data Pipeline Design

- Compile search terms 
- Assess search term relevance [litsearchr]
  - Access literature [rcrossref]
- Search literature [EBSCO Search Premier]
- Analyze literature results [bibliometrix]
  - Analyze content for intersection with Hawai‘i agriculture
  - Key cross-terms: tropic, hawaii, pacific, island, ... 
- Create a dashboard [Shiny]
- Host dashboard [RShiny]

# Search Terms

Develop a list from the most recent reviews of climate smart
agriculture. 

- climate smart agriculture
- csa
- climate smart commodity
- csc
- climate change
- agroecology
- sustainable agriculture
- nrcs
- conservation
- soil health

```{r setup, echo = FALSE}

library(pacman)
p_load(litsearchr, rcrossref, purrr)
## p_load(litsearchr, rcrossref, purrr, bibliometrix)


```


## rcrossref

https://docs.ropensci.org/rcrossref/articles/rcrossref.html

```{r cr-example, cache = TRUE}

qs <- c("climate smart agriculture")
res <- cr_works(query = qs, limit = 100) %>% pluck("data")
names(res)

```

## *litsearchr* workflow

1. Identifies potential keywords through the naive search input
2. Builds a keyword co-occurrence network to increase search precision
3. Uses a cutoff function to identify keyword importance
4. Assists with grouping terms into concepts
5. Writes a Boolean search 

https://luketudge.github.io/litsearchr-tutorial/litsearchr_tutorial.html


```{r litsearchr, cache = TRUE}


```

## Webcrawling

https://github.com/salimk/Rcrawler
https://ladal.edu.au/webcrawling.html#Following_links


# analysis

bibliometrix


## R Tools

- https://elizagrames.github.io/litsearchr/#tutorials 
- https://www.bibliometrix.org/home/index.php/layout/bibliometrix 
- https://www.harc-hspa.com/climate-smart-agriculture.html 
- https://github.com/elizagrames/topictagger 
- https://github.com/cran/metagear 
- https://cran.r-project.org/web/packages/scholar/index.html 

