---
title: Literature Review - Climate Smart Ag Links to Ecosystem Services
author: MK Lau
---


# Context

The City and County of Honolulu's Office of Climate Resilience has
contracted OACA to produce a Climate Smart Agriculture database
intended to inform food system professionals and policy makers on the
potential ecosystem service impacts of CSA activities. The consultant
(MK Lau) has been sub-contracted by OACA to complete the deliverables
listed below in partial fulfillment of the larger contracted
deliverable to HC&C.


# Key Personnel

*Dr. Matthew Kekoa Lau, PhD.* -- will combine his expertise in
ecological systems theory and big data analysis with the practice of
sustainable agriculture to produce the contracted deliverables.

# Deliverables

- CSA-ES literature synthesis
- CSA-ES Resource Database

# Data Pipeline Design

- Compile search terms 
- Assess search term relevance [litsearchr]
  - Access literature [rcrossref]
- Search literature [EBSCO Search Premier]
- Analyze literature results [bibliometrix]
  - Analyze content for intersection with Hawai‘i agriculture
  - Key cross-terms: tropic, hawaii, pacific, island, ... 
- Create a dashboard [Shiny]
- Host dashboard [RShiny]

# Search Terms

Terms for practices to focus searches on was generated from the NRCS
CSAF Mitigation Strategies 2024 list:

- [NRCS](https://www.nrcs.usda.gov/sites/default/files/2023-10/NRCS-CSAF-Mitigation-Activities-List.pdf)

Other potential sources of practices could be: 

- [CSA](https://www.nrcs.usda.gov/conservation-basics/natural-resource-concerns/climate/climate-smart-mitigation-activities)
- [CSC](https://www.usda.gov/climate-solutions/climate-smart-commodities "CSC")

Policy information can be obtained from the FAO databases: 

- [FAO](https://fapda.apps.fao.org/fapda/#main.html "FAO Food and Agriculture")
- [FAOForestry](https://www.fao.org/in-action/fapda/forestry-tool/policies/en/ "FAO Forestry Database")

Urban Database for policy information: 

[Urban](https://foodsystemsplanning.ap.buffalo.edu/resources/global-database-for-food-policies/adv-search-gfpd/ "University of Buffalo City and Regional Food Policy Database")

Other government data:

[GovData](https://www.fsa.usda.gov/online-services/fsa-online-data-resources/index "Other Government Data")


```{r setup, echo = FALSE}

library(pacman)
p_load(litsearchr, rcrossref, purrr, wordcloud, 
       tm, RColorBrewer, ggplot2, Rcrawler, rvest, 
       knitr)

```


## rcrossref

https://docs.ropensci.org/rcrossref/articles/rcrossref.html

```{r cr-example, cache = TRUE}

qs <- c("climate smart agriculture")
res <- cr_works(query = qs, limit = 1000) %>% pluck("data")
head(res)

```

```{r csa-wc, echo = FALSE}

rmSW <- function(x, sw, replace = ""){
    if (x %in% sw){
        out <- replace
    }else{
        out <- x
    }
    return(out)
}

## csa.abs <- na.omit(res[["abstract"]]) %>% 
##     paste(collapse = " ")

##     gsub("<[^>]+>", "")

csa.ti <- res[["title"]] %>% 
    tolower %>% 
    gsub(pattern = "[][!#$%()*,.:;<=>@^_|~.{}]", replacement = "")  %>% 
    na.omit %>% 
    strsplit(split = " ")  %>%
    unlist  
csa.ti <- sapply(csa.ti, rmSW, sw = stopwords("english")) 
csa.ti <- csa.ti[csa.ti != ""]
csa.tab <- table(csa.ti)


```{r wc.plot, echo = FALSE}

wordcloud(words = names(csa.tab), freq = csa.tab, min.freq = 10,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

```{r bar.plot, echo = FALSE}

data <- data.frame(
  category = c("Ecosystem", "Services"),
  value = c(csa.tab["ecosystem"], csa.tab["services"])
)

ggplot(data, aes(x = category, y = value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "",
       x = "",
       y = "Occurrences")

```


## *litsearchr* workflow

1. Identifies potential keywords through the naive search input
2. Builds a keyword co-occurrence network to increase search precision
3. Uses a cutoff function to identify keyword importance
4. Assists with grouping terms into concepts
5. Writes a Boolean search 

https://luketudge.github.io/litsearchr-tutorial/litsearchr_tutorial.html


```{r litsearchr, cache = TRUE}


```

## Webcrawling

https://github.com/salimk/Rcrawler
https://ladal.edu.au/webcrawling.html#Following_links


```{r crawl-nrcs, cahce = TRUE, eval = TRUE}

if ("nrcs-usda-gov-030004.Rdata" %in% dir("./data/")){
    load("data/nrcs-usda-gov-030004.Rdata")
}else{
    Rcrawler(Website = "https://www.nrcs.usda.gov/conservation-basics/natural-resource-concerns/climate/climate-smart-mitigation-activities",
             no_cores = 4, no_conn = 4, 
             NetworkData = TRUE,
             ExtractXpathPat = "//*/a/@href",
             ManyPerPattern = TRUE, MaxDepth = 2, 
             )
}

nrc.url <- INDEX[INDEX[, "Level"] == 2, "Url"]
nrc.url <- nrc.url[grepl("natural-resource-concerns/", nrc.url)]
nrc.cat <- strsplit(nrc.url, "natural-resource-concerns/")
nrc.url <- nrc.url[lapply(nrc.cat, length) == 2]
nrc.cat <- nrc.cat[lapply(nrc.cat, length) == 2]
nrc.cat <- lapply(nrc.cat, function(x) x[2])
nrc.cat <- lapply(nrc.cat, strsplit, split = "\\/")
nrc.cat <- lapply(nrc.cat, unlist)

for (i in seq_len(length(nrc.cat))){
    if (length(nrc.cat[[i]]) < max(unlist(lapply(nrc.cat, length)))){
        nrc.cat[[i]] <- c(nrc.cat[[i]], rep("", times = max(unlist(lapply(nrc.cat, length))) - length(nrc.cat[[i]])))
    }else{}
}

nrc.tab <- cbind(do.call(rbind, nrc.cat), nrc.url)
colnames(nrc.tab) <- c("Category", 
                       paste0("Sub-Category ", seq(1, ncol(nrc.tab)-2)),
                       "Resource")


```


Data from [NRCS](https://www.nrcs.usda.gov/sites/default/files/2023-10/NRCS-CSAF-Mitigation-Activities-List.pdf)
were extracted manually using [tabula](https://tabula.technology/ "tabula").

```{r nrcs-pdf-tables, }

csa.mit.tab <- read.csv("data/tabula-NRCS-CSAF-Mitigation-Activities.csv", header = FALSE)
csa.mit.head <- csa.mit.tab[grepl("Mitigation Categories", csa.mit.tab[, 1]), ]
csa.mit.head <- gsub("\\[.*?\\]", "", csa.mit.head)
csa.mit.head <- gsub("  ", " ", csa.mit.head)
colnames(csa.mit.tab) <- csa.mit.head
csa.mit.tab <- apply(csa.mit.tab, 2, gsub, pattern = "\\[.*?\\]", replace = "")
csa.mit.tab <- apply(csa.mit.tab, 2, gsub, pattern = "  ", replace = " ")

## Removing narrative crosswalk
csa.cwk <- csa.mit.tab[seq(grep("Waste Storage Structure", csa.mit.tab[, 2]), nrow(csa.mit.tab)), ]
colnames(csa.cwk)[4] <- "Narrative"
csa.mit.tab <-csa.mit.tab[-seq(grep("Waste Storage Structure", csa.mit.tab[, 2]), nrow(csa.mit.tab)), ]

## Generate urls for codes
csa.mit.tab[!(grepl("E", csa.mit.tab[, "Code"])), "Code"] <- ""
csa.mit.url <- paste0("https://www.nrcs.usda.gov/sites/default/files/2022-11/", 
                      csa.mit.tab[, "Code"],
                      "_July_2022.pdf")
csa.mit.url <- gsub(" ", "-", csa.mit.url)
csa.mit.url[csa.mit.tab[, "Code"] == ""] <- ""
csa.mit.tab <- data.frame(csa.mit.tab, "URL" = csa.mit.url)

```


```{r csa-table, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

kable(nrc.tab)

```

```{r mit-table, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

kable(csa.mit.tab)

```



# analysis

- policy 
- farming practices
- databases
- tropics
- ecosystem services

[Bibliometrix](https://www.bibliometrix.org/home/index.php/layout/bibliometrix  "Bibliometrix")


## R Tools

- https://elizagrames.github.io/litsearchr/#tutorials 
- https://www.bibliometrix.org/home/index.php/layout/bibliometrix 
- https://www.harc-hspa.com/climate-smart-agriculture.html 
- https://github.com/elizagrames/topictagger 
- https://github.com/cran/metagear 
- https://cran.r-project.org/web/packages/scholar/index.html 

